A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation

### 2016-07-19 crystal-gel/nature/Supplementary.tex

\centerline{\bf \large Supplementary Information for}
\centerline{\bf \large``A novel route to the spontaneous formation of porous crystals via}
\centerline{\bf \large viscoelastic phase separation''}
\vspace{0.5cm}

@@

\begin{figure*}[!t]
\includegraphics{capillary.pdf}
\caption{\textbf{Capillary experiment reproducing the crystal-gel state.} The colloid volume fraction is $\approx 0.33$ and the polymer concentration is $0.40\,$mg/g. Top row: Confocal slices showing the initial network, crystallising network and final crystal-gel network. Bottom row: Reconstructions from confocal coordinates. Particles are drawn to scale and coloured according to their phase. Red: crystal; white: liquid; green: gas. To highlight the crystalline regions, liquid and gas particles are drawn to a tenth of the crystalline particle size.}
\label{fig:capillary}
\end{figure*}

The use of a reservoir of a salt solution through a semi-permeable membrane, allowed us to follow the entire microscopic dynamics in absence of spurious flows, from the first stages of phase separation to the formation of the crystal-gel state. In order to confirm the reproducibility of the crystal-gel state, we conducted experiments in a more traditional capillary setting, where all components of the suspension are pre-mixed in a sealed cell. A typical example is
shown in Fig.~\ref{fig:capillary}, where a system with the colloid volume fraction of $\approx 0.33$ and the polymer concentration of $0.40\,$mg/g is considered.
The figure shows the time evolution of the sample at three different times, just after phase separation ($t=340\,\tau_{\rm B}$), and during
crystal-gel formation ($t=2600\,\tau_{\rm B}$ and $t=6650\,\tau_{\rm B}$). The top-row shows images from quasi two-dimensional confocal slices, while the bottom-row shows
the three-dimensional reconstruction after single-particle tracking, where crystalline particles are highlighted in both size (large) and color (red).

@@

>>>>

\centerline{\bf \large Supplementary Information for}
\centerline{\bf \large``A novel physical mechanism for the spontaneous formation }
\centerline{\bf \large of porous crystals via viscoelastic phase separation''}
\vspace{0.5cm}

@@

\begin{figure*}[!t]
\includegraphics{capillary.pdf}
\caption{\textbf{Capillary experiment reproducing the crystal-gel state.} The colloid volume fraction is $\approx 0.33$ and the polymer concentration is $0.40\,$mg/g. Top row: Confocal slices showing the initial network, crystallising network and final crystal-gel network. Bottom row: Reconstructions from confocal coordinates. Particles are drawn to scale and coloured according to their phase. Red: crystal; white: liquid; green: gas; surface: blue. To highlight the crystalline regions, liquid, gas, surface particles are drawn to a tenth of the crystalline particle size.}
\label{fig:capillary}
\end{figure*}

The use of a reservoir of a salt solution through a semi-permeable membrane, allowed us to follow the entire microscopic dynamics in absence of spurious flows, from the first stages of phase separation to the formation of the crystal-gel state. In order to confirm the reproducibility of the crystal-gel state, we conducted experiments in a more traditional capillary setting, where all components of the suspension are pre-mixed in a sealed cell. A typical example is
shown in Fig.~\ref{fig:capillary}, where a system with the colloid volume fraction of $\approx 0.33$ and the polymer concentration of $0.40\,$mg/g is considered.
The figure shows the time evolution of the sample at three different times, just after phase separation ($t=340\,\tau_{\rm B}$), and during
crystal-gel formation ($t=2600\,\tau_{\rm B}$ and $t=6650\,\tau_{\rm B}$). The top-row shows images from quasi two-dimensional confocal slices, while the bottom-row shows
the three-dimensional reconstruction after single-particle tracking, where crystalline particles are highlighted in both size (large) and color (red), surface particles
are depicted in blue, gas in green and liquid in white.

@@

\section*{Supplementary Movie 3}
Same as Supplementary Movie 2, but with computer rendered trajectories obtained from the tracking of the colloidal particles. Particles are coloured according to the following code: crystal (red), surface (blue), gas (green) and liquid (white). For display purposes, crystalline particles and gas particles are respectively 400\% and 50\% bigger than other particles (liquid or surface).
